MLCommons Earthquake Science Benchmark

### 2022-02-24 paper-capstone-earthquake.tex
Updates from Overleaf

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         1 &   
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 & 
         1 & 
         Sep 2021   \\
            & 
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H &  1 &   NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  1 &   NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & Rob.K & AMD Ryzen 9 5900HX & 1 &  NVidia RTX 3080 &  16GB & 1 & 1 & 11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\BIOFIG{images/bio/gregor.png}{Thomas Butler}{is a Graduate Student at
  University of Virginia's School of Data Science. His undergraduate
  degree is in Biomedical engineering. He has over eight years of
  experience in the Infertility field helping patients, jointly
  running a Andrology lab, and contributing research to advance the
  field through joint research on how AMH effects pregnancy outcomes
  and sperm antibodies effect PSA. He has a certificate in Data
  Analytics from Georgia Institute of Technology.}

@@

\BIOFIG{images/bio/fox.png}{Geoffrey C. Fox}{TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD}

@@

\item build docker container image that can run python 3.9.7 and conda
\item verified access to GPU allocations in Rivanna

>>>>

\section{Earthquake Data}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         1 &   
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 & 
         1 & 
         Sep 2021   \\
            & 
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         Table \ref{tab:tcompute}   & Thomas.A  & i7-8750H &  1 & \href{https://www.gigabyte.com/Laptop/AERO-15--RTX-20-Series#kf}{NVIDIA GeForce RTX 2070 with Max-Q Design} & 16GB & 1 & 1 & Jan 2019   \\
         \hline
         Table \ref{tab:rcompute} & Rob.K & AMD Ryzen 9 5900HX & 1 &  \href{https://rog.asus.com/us/laptops/rog-strix/2021-rog-strix-scar-15-series/}{NVidia RTX 3080} &  16GB & 1 & 1 & 11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\BIOFIG{images/bio/tom.png}{Thomas Butler}{is a Graduate Student at
  University of Virginia's School of Data Science. His undergraduate
  degree is in Biomedical engineering. He has over eight years of
  experience in the Infertility field helping patients, jointly
  running a Andrology lab, and contributing research to advance the
  field through joint research on how AMH effects pregnancy outcomes
  and sperm antibodies effect PSA. He has a certificate in Data
  Analytics from Georgia Institute of Technology.}

@@

\BIOFIG{images/bio/fox.png}{Geoffrey C. Fox}{is a computational and data 
  science professor for University of Virginia. He has over 50 years of 
  experience in 'big data' and high-performance computing. Through his 
  career, he has contributed to these fields in both research and education 
  the next generation. In 2019 he received the ACM-IEEE CS Ken Kennedy 
  award for his work in parallel computing methodology, algorithms and 
  software, data analysis, and how these interface with broad classes of 
  applications. His current research interests are exploring the various 
  use cases of neural networks.}

@@

\item build docker container image that can run python 3.9.7 and conda
\item verified access to GPU allocations in Rivanna
\item created a portable version of python 3.10.2 that can run on Rivanna \GITPULL{8}
\item implemented cloudmesh-data (\href{https://github.com/cloudmesh/cloudmesh-data/pull/1}{cloudmesh/cloudmesh-data PR 1}, \href{https://github.com/cloudmesh/cloudmesh-data/pull/3}{cloudmesh/cloudmesh-data PR #3})
